\begin{center}
{\bfseries\fontsize{16}{18}\selectfont ACKNOWLEDGEMENT}
\end{center}

\vspace{0.5cm}
\noindent
It is with immense pleasure that I would like to express my indebted gratitude to my project supervisor,
Mr. Alla Rajendra, who has guided me a lot and encouraged me in every step of project work.
His valuable moral support and guidance has been helpful in successful completion of this project.

\vspace{0.3cm}

\noindent
I wish to express my sincere thanks to Dr. CHAKKA S.V.S.N. Murty, Head of the Department of CSE,
for his valuable guidance given to me throughout the period of the project work.

\vspace{0.3cm}

\noindent
I feel elated to thank Principal, Dr. A. RAMESH, of Aditya College of Engineering and Technology
for his cooperation in completion of my project and throughout my course.

\vspace{0.3cm}

\noindent
I feel elated to thank Dr. Pullela S.V.S.S. Ravi Kumar, Dean (Academics) of Aditya College of Engineering and Technology (A)
for his cooperation in completion of my project.

\vspace{0.3cm}

\noindent
I wish to express my sincere thanks to all faculty members and lab programmers for their valuable guidance
given to me throughout the period of the project.

\vspace{0.3cm}

\noindent
I avail this opportunity to express my deep sense and heartfelt thanks to the Management of
Aditya College of Engineering \& Technology (A) for providing great support for me by arranging the trainees,
and facilities needed to complete my project and for giving me the opportunity for doing this work.

\vspace{2cm}

\begin{flushright}
\textbf{PROJECT ASSOCIATE}\\[0.5cm]

ANKIT ROY CHOWDHURY (22P31A0504)
\end{flushright}