\chapter{Conclusion}

The SafeSurf project presents a comprehensive solution for real-time phishing website detection using a hybrid machine learning approach \cite{ref1}. The system is designed with a multi-layered architecture that combines structured feature analysis, natural language processing, and efficient backend integration to deliver accurate and reliable predictions.

A key strength of SafeSurf lies in its ensemble-based methodology. Instead of relying on a single model, the system integrates multiple machine learning algorithms such as Logistic Regression, Support Vector Machine, Random Forest, HistGradientBoosting, and XGBoost within a VotingClassifier framework. This is further enhanced by an NLP-based Logistic Regression model that analyzes lexical patterns using Bag-of-Words representation. This combination improves generalization, reduces false predictions, and enhances the detection of both simple and sophisticated phishing attacks.

The system architecture is optimized for real-time performance. The DNS Guard layer acts as an initial filter, instantly blocking invalid or non-existent domains and reducing unnecessary computation. In addition, asynchronous feature extraction enables efficient processing of 111 features, including lexical, network, and textual attributes, ensuring a balance between accuracy and response time. Threshold-based decision logic further improves classification reliability.

The system also focuses on usability and real-world applicability. A React-based web interface and a Chrome extension allow users to analyze URLs seamlessly during browsing. The output is simplified to display clear results such as \textit{Safe} or \textit{Phishing Risk}, ensuring accessibility for non-technical users while maintaining system effectiveness.

Throughout development, the system demonstrated stable performance across different types of URLs. The combination of ensemble learning and feature engineering contributed to improved robustness and adaptability to evolving phishing techniques.

Overall, SafeSurf provides a scalable, efficient, and intelligent framework for phishing detection. The integration of machine learning models, system-level optimizations, and user-centric design makes it a strong foundation for future enhancements such as cloud deployment, continuous model updates, and advanced threat detection mechanisms.