\begin{center}
{\bfseries\fontsize{16}{18}\selectfont ABSTRACT}
\end{center}

\addcontentsline{toc}{chapter}{ABSTRACT}

\vspace{0.5cm}

\noindent
\textbf{SafeSurf — A Machine Learning-Based Real-Time Phishing Website Detector}

\vspace{0.5cm}

\noindent
Phishing attacks remain a significant cybersecurity threat, targeting users through deceptive websites that mimic legitimate platforms to steal sensitive information. Rapid and accurate detection of such malicious websites is therefore essential for ensuring safe online interactions. This project presents \textbf{SafeSurf}, a real-time phishing website detection system based on supervised machine learning techniques. The system analyzes multiple URL and website characteristics—including domain attributes, HTTPS usage, URL length, and structural HTML indicators—to effectively distinguish between phishing and legitimate websites.

\vspace{0.3cm}

\noindent
Unlike traditional blacklist-based approaches, which often fail to detect newly generated phishing domains, \textbf{SafeSurf} employs data-driven learning methods trained on a dataset of phishing and benign URLs. The system incorporates preprocessing techniques such as handling missing values, feature normalization, and noise reduction to improve model reliability. Feature importance analysis is used to identify key indicators associated with phishing activity, while an ensemble-based machine learning approach combines multiple classification models to improve detection performance and robustness.

\vspace{0.3cm}

\noindent
Experimental results show that the proposed system achieves high detection accuracy ($> 97\%$) with efficient prediction time, making it suitable for real-time applications. By integrating machine learning with automated feature analysis, \textbf{SafeSurf} provides a scalable and adaptive solution for phishing detection and helps strengthen cybersecurity by reducing users’ exposure to malicious websites.

\vspace{1cm}

\noindent
\textbf{Mentor:} Mr. Alla Rajendra\\
\textbf{Batch No:} 16\\
\textbf{Batch Members:}

\vspace{0.2cm}

\noindent
YALLAPRAGADA OMTEJA (22P31A0539)\\
KARRI DEEPIKA (22P31A0517)\\
DANGETI SAI GAYATRI VISHWESH (22P31A0508)\\
ANKIT ROY CHOWDHURY (22P31A0504)

\vspace{1.5cm}

\begin{flushright}
\textbf{Guide Signature}
\end{flushright}