\begin{center}
{\bfseries\fontsize{16}{18}\selectfont ACKNOWLEDGEMENT}
\end{center}

\vspace{0.5cm}
\noindent
It is with immense pleasure that we would like to express our indebted gratitude to our project supervisor,
Mr. Alla Rajendra, who has guided us a lot and encouraged us in every step of project work.
His valuable moral support and guidance has been helpful in successful completion of this project.

\vspace{0.3cm}

\noindent
We wish to express our sincere thanks to Dr. CHAKKA S.V.V.S.N. Murty, Head of the Department of CSE,
for his valuable guidance given to us throughout the period of the project work.

\vspace{0.3cm}

\noindent
We feel elated to thank Principal, Dr. A. RAMESH, of Aditya College of Engineering and Technology
for his cooperation in completion of our project and throughout our course.

\vspace{0.3cm}

\noindent
We feel elated to thank Dr. Pullela S.V.S.S. Ravi Kumar, Dean (Academics) of Aditya College of Engineering and Technology (A)
for his cooperation in completion of our project.

\vspace{0.3cm}

\noindent
We wish to express our sincere thanks to all faculty members and lab programmers for their valuable guidance
given to us throughout the period of the project.

\vspace{0.3cm}

\noindent
We avail this opportunity to express our deep sense and heartfelt thanks to the Management of
Aditya College of Engineering \& Technology (A) for providing great support for us by arranging the trainees,
and facilities needed to complete our project and for giving us the opportunity for doing this work.

\vspace{2cm}

\begin{flushright}
\textbf{PROJECT ASSOCIATES}\\[0.5cm]

YALLAPRAGADA OMTEJA (22P31A0539)\\
KARRI DEEPIKA (22P31A0517)\\
DANGETI SAI GAYATRI VISHWESH (22P31A0508)\\
ANKIT ROY CHOWDHURY (22P31A0504)
\end{flushright}