\chapter{Future Scope}

The SafeSurf system provides a strong foundation for real-time phishing detection using machine learning. However, there are several areas where the system can be further enhanced to improve its capabilities, scalability, and real-world applicability.

One of the primary areas of improvement is cloud-based deployment. Deploying the system on platforms such as AWS or Google Cloud would enable high availability, better scalability, and support for handling large volumes of real-time requests \cite{ref14}. Integration with container orchestration tools can further improve system reliability and performance.

Another important enhancement is continuous model improvement. The phishing landscape is constantly evolving, and attackers use increasingly sophisticated techniques. Incorporating automated data collection and periodic model retraining will help the system adapt to new phishing patterns and maintain high detection accuracy over time.

Enhancements in feature extraction can also be explored. Incorporating deeper content-based analysis, such as webpage structure, JavaScript behavior, and visual similarity detection, can help identify advanced phishing attacks that mimic legitimate websites more closely.

From a user experience perspective, the system can be improved by developing a more interactive dashboard. Features such as detection history, risk analytics, and user alerts can provide better insights and improve usability. Mobile compatibility and browser-wide integration can further enhance accessibility.

Security improvements are another key area for future development. Implementing authentication mechanisms such as JWT, role-based access control, and HTTPS enforcement will ensure secure communication and protect the system from misuse.

Finally, the system can be expanded into a fully autonomous cybersecurity tool by integrating real-time monitoring, automated reporting, and adaptive decision-making mechanisms. This would enable SafeSurf to function not only as a detection system but also as a proactive defense solution against phishing threats.

In conclusion, the proposed future enhancements aim to transform SafeSurf into a more scalable, adaptive, and intelligent cybersecurity solution capable of addressing modern phishing challenges effectively.